Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-10-06 article.tex
corrected convergence graph for Cooks membrane neo-hookean case
Add reminder for Rhie-Chow appendix
Updates to Sec 4.2

More generally,  linear momentum conservation can be expressed in a nonlinear geometry form, which is suitable for finite strains.
Two equivalent nonlinear geometry forms are common: the \emph{total} Lagrangian form:
\begin{eqnarray} \label{eqn:momentum_TL}
    \int_{\Omega_o} \rho_o \frac{\partial^2 \bb{u} }{\partial t^2} d\Omega_o
    =
    \oint_{\Gamma_o} \left( J \bb{F}^{-T} \cdot \bb{n}_o \right) \cdot \bb{\sigma} \ d\Gamma_o
    + \int_{\Omega_o}  \rho_o \bb{g} \, d\Omega_o
\end{eqnarray}
and the \emph{updated} Lagrangian form:
\begin{eqnarray} \label{eqn:momentum_UL}
    \int_{\Omega_u} \frac{\partial }{\partial t} \left( \rho_u \frac{\partial \bb{u} }{\partial t} \right) d\Omega_u
    = \oint_{\Gamma_u}(j\bb{f}^{-T}\cdot{\bb{n}_u)\cdot \bb{\sigma}}\ d\Gamma_u
    + \int_{\Omega_u}  \rho_u \bb{g} \, d\Omega_u
\end{eqnarray}
where subscript $o$ indicates quantities in the initial reference configuration, and subscript $u$ indicates quantities in the updated configuration.
The true (Cauchy) stress tensor is indicated by $\bb{\sigma}$.

@@

This section assesses the performance of the proposed Jacobian-free Newton-Krylov solution approach on several benchmark cases.
The cases have been chosen to exhibit a variety of characteristics in terms of
\begin{itemize}
	\item Geometric dimension (2-D vs. 3-D),
	\item Geometric nonlinearity (small strain vs. large strain)
	\item Statics vs. dynamics, and
	\item Material behaviour (elasticity, elastoplasticity, hyperelasticity).
\end{itemize}

In addition, through the analysis of the benchmark cases above, the effect of several parameters will be examined, including the mesh types, Rhie-Chow stabilisation scaling, preconditioner choices, linear solver settings, the effect of globalisation strategies, and multi-CPU-core parallelisation.
The performance of the Jacobian-free Newton-Krylov algorithm is compared with that of the segregated algorithm in terms of computational time and memory requirements.
Metrics from a commercial finite element software (Abaqus) are included for reference \hl{ask Dylan to run Abaqus cases once we have our results}.

@@

Figure \ref{fig:cooksMembrane_disp} compares the predicted vertical displacement at the reference point as a function of the average cell widths with results from the literature.
The reference point is taken as the top right point -- (48,60) mm -- in the elastic and hyperelastoplastic cases, while it is taken as the midway point of the loading surface -- (48,52) mm -- in the hyperelastic case.
%\hl{Comment on results -> good/bad/etc}
%\hl{Comment on JFNK not working for plasticty}\\
%\hl{Philip, I'll leave this to you to comment on, as you'll be able to explain it better.}
\begin{figure}[htbp]
   \centering
   	\subfigure[Linear elastic case]
	{
		\includegraphics[width=0.45\textwidth]{figures/cooksMembrane-hookeanTipDispConvergence}  
	}
	\subfigure[Hyperelastic case \hl{Update @Ivan}]
	{
		\includegraphics[width=0.45\textwidth]{figures/cooksMembrane-neoHookeanTipDispConvergence}  
	}
	\subfigure[Hyperelastoplastic case \hl{@Ivan: we need to get closer agreement}]
	{
		\includegraphics[width=0.45\textwidth]{figures/cooksMembrane-neoHookeanPlasticTipDispConvergence}  
	}
%	\subfigure[Equivalent stress distribution for the hyperelastic case (case ii) using the mesh with $36\,842$ cells]
%	{
%		\includegraphics[height=0.5\textwidth]{figures/cooksMembrane-sigmaEq.pdf}  
%	}
%	\subfigure[Convergence of tip (48,60) vertical displacement, normalised using the displacement value from the finest mesh (given in parentheses)]
%	{
%		\includegraphics[height=0.35\textwidth]{figures/cooksMembrane-tipDispConvergence.pdf} 
%	}
   \caption{Cook's membrane vertical displacement predictions at the reference point as a function of the average cell width. Comparisons are given with the results from \cite{Zienkiewicz2000, Pelteret2018, Simo1992, Simplas}.}
   \label{fig:cooksMembrane_disp}
\end{figure}

@@

\paragraph{Case 6: Vibration of a 3-D Cantilevered Beam}
This 3-D, dynamic, finite strain case geometry consists of a $2 \times 0.2 \times 0.2$ m cuboid column and was proposed in its initial form by \citet{Tukovic2007}.
%(Figure \ref{fig:dynamic_cantilever})
%A sudden, constant traction $\bb{T} = \left(\sfrac{|\bb{T}|}{\sqrt{2}}\right) \left(1, 1, 0 \right)$ Pa is applied to the upper surface, where the magnitude $|\bb{T}|$ is defined in terms of a dimensionless load factor $\mathcal{F}$ as
%\begin{eqnarray}
%	|\bb{T}| = \frac{\mathcal{F} E I}{A L^2} \text{ Pa}
%\end{eqnarray}
A sudden, constant traction $\bb{T} = \left(0.1, 0.1, 0 \right)$ MPa is applied to the upper surface.
%A sudden, constant traction $\bb{T} = \left(\sfrac{|\bb{T}|}{\sqrt{2}}\right) \left(1, 1, 0 \right)$ Pa is applied to the upper surface, where the magnitude $|\bb{T}|$ is defined in terms of a dimensionless load factor $\mathcal{F}$ as
%In the current study, $\mathcal{F} = 1$.
A neo-Hookean hyperelastic material is assumed with $E = 15.293$ MPa, $\nu = 0.3$ and density $\rho = 1000$ kg m$^{-3}$, while the area $A = 0.04$ m$^2$ and the second moment of area $I = \frac{1}{7\,500}$ m$^4$. %0.0001333
The geometric and material parameters were chosen for the first natural frequency to be 1 Hz in the small strain limit.
The magnitude of the applied traction was chosen to ensure significant geometric nonlinearity with the upper surface of the beam expected to drop below the plane of the lower surface.
Four succesively refined hexahedral meshes are generated using the OpenFOAM \texttt{blockMesh} utility, with cell counts of 270, $2\,160$, $17\,280$ and $138\,240$.
%A fixed time step size of 0.001617274174 s is chosen, corresponding to a Courant number of six on the mesh with $2\,160$ cells.
%A fixed time step size of 1 ms is chosen.
The time step size is 1 ms, and the total period is 10 s.
% corresponding to 10 expected oscillation periods.
%, corresponding to a Courant number of six on the mesh with $2\,160$ cells.

The deformed configuration of the beam at six time steps is shown in Figure \ref{fig:dynamic_cantilever}(a) for the mesh with $2\,160$ cells, where the upper surface is seen to drop below the horizontal from approximately t = 0.2 s to 0.32 s.
The corresponding displacement magnitude of the centre of the upper surface of the beam vs time is shown in Figure \ref{fig:dynamic_cantilever}(b).
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.5\textwidth]{figures/cantilever} 
	\subfigure[Displacement magnitude for t = $\left\{0, \, 0.1, \, 0.2\right\}$ s (translucent) and t = $\left\{0.3, \, 0.4, \, 0.5 \right\}$ s (opaque) for the mesh with $138\,240$ cells]
	{
	   \includegraphics[width=0.4\textwidth]{figures/cantilever_deformed}
   	} \quad
	\subfigure[Displacement magnitude of the centre of the upper surface of the beam vs time]
	{
	   \includegraphics[width=0.5\textwidth]{figures/cantilever_disp} 
   	   %\includegraphics[height=0.45\textwidth]{figures/cantilever_sigmaEq}  
   	}
   \caption{Deflection of a 3-D Cantilevered Beam}
   \label{fig:dynamic_cantilever}
\end{figure}
\hl{It would be good to add a reference results, e.g. from FE}

@@

\hl{maybe we should state the nonlinear/linear solver settings for completeness}

\paragraph{Case 7: Axial Turbine Blade}
\hl{Solve statically}
This 3-D, dynamic, finite strain case geometry consists of a twisted axial turbine blade, 0.8 m in height, with a cord length of 0.2 m (Figure \ref{fig:turbine_blade}), and is taken from \citet{Tukovic2007}.
\hl{Zeljko probably has this geometry or a reference for where it came from}
The blade is constrained at one end and subjected to a sudden, constant traction of $\bb{T} = ($\hl{ZZZ,ZZZ,ZZZ}$)$ Pa at the other end.
A St.\ Venant-Kirchoff material is assumed with $E = 15.293$ MPa and $\nu = 0.3$, while the area $A = (0.2)(0.2) = 0.04$ m$^2$ and the second moment of area $I = 0.0001333$ m$^4$.
\hl{Comment on the meshes}
A fixed time step size of \hl{XXX} s is chosen, corresponding to a \hl{YY} on the coarsest mesh \hl{update as required}.
The total time period is \hl{XXX} s, corresponding to \hl{XX} expected oscillation periods.
%\hl{An advantage of this case over the cantilever is that it is complex geometry; a disadvantage is that we do not have a reference solution}
%\hl{A mitigation for this disadvantage is we could run it in Abaqus to provide a credible reference}
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/turbine_blade.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Vibration of an axial turbine blade case geometry, mesh and loading conditions}
   \label{fig:turbine_blade}
\end{figure}

@@

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Robustness and Resource Requirements}
\label{sec:resource_requirements}
%%--------------------------------------------------------------------------------------------------------------------%%
This section compares the robustness and resource requirements of the Jacobian-free Newton-Krylov and segregated approach on the cases presented in Section \ref{sec:accuracy}.
Specifically, cases where either approach diverges are examined, and the time and memory requirements are presented.
In some cases, time and memory requirements from finite element procedures for reference.
Time and memory requirements are implementation and hardware-specific; nonetheless, it is insightful to see the relative performances of the Jacobian-free Newton-Krylov and segregated approaches on the same hardware and within the same implementation framework.
% where several mesh densities are examined.
%Time and memory requirements from the classic segregated approach are given for comparison, along with the requirements from commercial finite element software Abaqus (version XXX): \hl{ask Dylan to create the Abaqus results when we are happy the paper will not change}.
%The finite element approach uses a coupled solution algorithm and direct linear solver, where a Newton-Raphson method is used for resolving nonlinearities.
%\hl{Take care when comparing times between different hardware}

Table \ref{tab:times_memory} lists the wall clock times (time according to a clock on the wall, rounded to the nearest second) and maximum memory usage according to the GNU time utility.
All clock times and memory usage were generated using a Mac Studio with an M2 Ultra CPU on one CPU core, where the code was built with the Clang compiler.
\hl{Present data for one hardware first, and give comparison after.}
Examination of multi-CPU-core parallelisation is left to Section \ref{sec:parallelisation}.
\begin{table}[htb]
	\centering
		\begin{tabular}{ll|ll|ll}
			\hline
			Case & Cell Count & \multicolumn{2}{c|}{JFNK} & \multicolumn{2}{c}{Segregated} \\
			     &            & Time (s) & Memory (MB) & Time (s) & Memory (MB) \\
			\hline 
			MMS & 384 & 0 & $78$ & X & Y \\
				& $4\,374$ & 0 & $86$ & X & Y \\
				& $41\,154$ & 1 & $195$ & X & Y \\
				&  $355\,914$ & 4 & $1\,063$ & X & Y \\
				& $2\,958\,234$ & 41 & $6\,724$ & X & Y \\
				& $24\,118\,074$ & 486 & $30\,606$ & X & Y \\
			\hline
			Elliptic & 45 & 0 & $72$ & X & Y \\
				& 472 & 0 & $78$ & X & Y \\
				& $4\,140$ & 1 & $153$ & X & Y \\
				& $34\,968$ & 7 & $754$ & X & Y \\
				& $287\,280$ & 95 & $3\,943$ & X & Y \\
				& $2\,438\,242$ & 988 & $21\,884$ & X & Y \\
			\hline
			T-member & 624& 0 & 84 & X & Y \\
				& $4\,992$ & 1 & 127 & X & Y \\
				& $39\,936$ & 10 & 557 & X & Y \\
				& $319\,488$ & 154 & $4\,024$ & X & Y \\
				& $2\,555\,904$ & $1\,751$ & $22\,814$ & X & Y \\
			\hline
			Ventricle & $1\,620$ & 54 & 133 & & \\
				& $12\,960$ & 576 & 553 & & \\
				& $103\,680$ & $8\,362$ & $3\,435$ & & \\
				& $829\,440$ & $150\,023$ & $11\,746$ & & \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage for Jacobian-free Newton-Krylov (JFNK) and segregated methods. Resource requirements are shown for the following cases: manufactured solution (MMS), XX }
	\label{tab:times_memory}
\end{table}

@@

>>>>

More generally,  linear momentum conservation can be expressed in a nonlinear geometry form, which is suitable for finite strains.
Two equivalent nonlinear geometry forms are common: the \emph{total} Lagrangian form:
\begin{eqnarray} \label{eqn:momentum_TL}
    \int_{\Omega_o} \rho_o \frac{\partial^2 \bb{u} }{\partial t^2} d\Omega_o
    =
    \oint_{\Gamma_o} \left( J \bb{F}^{-T} \cdot \bb{n}_o \right) \cdot \bb{\sigma} \ d\Gamma_o
    + \int_{\Omega_o}  \bb{f}_b \, d\Omega_o
\end{eqnarray}
and the \emph{updated} Lagrangian form:
\begin{eqnarray} \label{eqn:momentum_UL}
    \int_{\Omega_u} \frac{\partial }{\partial t} \left( \rho_u \frac{\partial \bb{u} }{\partial t} \right) d\Omega_u
    = \oint_{\Gamma_u}(j\bb{f}^{-T}\cdot{\bb{n}_u)\cdot \bb{\sigma}}\ d\Gamma_u
    + \int_{\Omega_u}  \bb{f}_b \, d\Omega_u
\end{eqnarray}
where subscript $o$ indicates quantities in the initial reference configuration, and subscript $u$ indicates quantities in the updated configuration.
The true (Cauchy) stress tensor is indicated by $\bb{\sigma}$.

@@

This section assesses the performance of the proposed Jacobian-free Newton-Krylov solution approach on several benchmark cases.
The cases have been chosen to exhibit a variety of characteristics in terms of
\begin{itemize}
	\item Geometric dimension (2-D vs. 3-D),
	\item Geometric nonlinearity (small strain vs. large strain),
	\item Geometric complexity (basic geometric shapes vs. complex geometry),
	\item Statics vs. dynamics, and
	\item Material behaviour (elasticity, elastoplasticity, hyperelasticity).
\end{itemize}

In addition, through the analysis of the benchmark cases above, the effect of several parameters will be examined, including the mesh types, Rhie-Chow stabilisation scaling, preconditioner choices, linear solver settings, the effect of globalisation strategies, and multi-CPU-core parallelisation.
The performance of the Jacobian-free Newton-Krylov algorithm is compared with that of the segregated algorithm in terms of computational time and memory requirements.
In all cases, the residuals are dropped by six orders of magnitude unless stated otherwise.
Metrics from a commercial finite element software (Abaqus) are included for reference \hl{ask Dylan to run Abaqus cases once we have our results}.

@@

Figure \ref{fig:cooksMembrane_disp} compares the predicted vertical displacement at the reference point as a function of the average cell widths with results from the literature.
The reference point is taken as the top right point -- (48,60) mm -- in the elastic and hyperelastoplastic cases, while it is taken as the midway point of the loading surface -- (48,52) mm -- in the hyperelastic case.
%\hl{Comment on results -> good/bad/etc}
%\hl{Comment on JFNK not working for plasticty}\\
%\hl{Philip, I'll leave this to you to comment on, as you'll be able to explain it better.}
\begin{figure}[htbp]
   \centering
   	\subfigure[Linear elastic case]
	{
		\includegraphics[width=0.45\textwidth]{figures/cooksMembrane-hookeanTipDispConvergence}  
	}
	\subfigure[Hyperelastic case]
	{
		\includegraphics[width=0.45\textwidth]{figures/cooksMembrane-neoHookeanTipDispConvergence}  
	}
	\subfigure[Hyperelastoplastic case \hl{@Ivan: we need to get closer agreement}]
	{
		\includegraphics[width=0.45\textwidth]{figures/cooksMembrane-neoHookeanPlasticTipDispConvergence}  
	}
%	\subfigure[Equivalent stress distribution for the hyperelastic case (case ii) using the mesh with $36\,842$ cells]
%	{
%		\includegraphics[height=0.5\textwidth]{figures/cooksMembrane-sigmaEq.pdf}  
%	}
%	\subfigure[Convergence of tip (48,60) vertical displacement, normalised using the displacement value from the finest mesh (given in parentheses)]
%	{
%		\includegraphics[height=0.35\textwidth]{figures/cooksMembrane-tipDispConvergence.pdf} 
%	}
   \caption{Cook's membrane vertical displacement predictions at the reference point as a function of the average cell width. Comparisons are given with the results from \cite{Zienkiewicz2000, Pelteret2018, Simo1992, Simplas}.}
   \label{fig:cooksMembrane_disp}
\end{figure}

@@

\paragraph{Case 6: Vibration of a 3-D Cantilevered Beam}
This 3-D, dynamic, finite strain case geometry consists of a $2 \times 0.2 \times 0.2$ m cuboid column and was proposed in its initial form by \citet{Tukovic2007}.
%(Figure \ref{fig:dynamic_cantilever})
%A sudden, constant traction $\bb{T} = \left(\sfrac{|\bb{T}|}{\sqrt{2}}\right) \left(1, 1, 0 \right)$ Pa is applied to the upper surface, where the magnitude $|\bb{T}|$ is defined in terms of a dimensionless load factor $\mathcal{F}$ as
%\begin{eqnarray}
%	|\bb{T}| = \frac{\mathcal{F} E I}{A L^2} \text{ Pa}
%\end{eqnarray}
A sudden, constant traction $\bb{T} = \left(0.1, 0.1, 0 \right)$ MPa is applied to the upper surface.
%A sudden, constant traction $\bb{T} = \left(\sfrac{|\bb{T}|}{\sqrt{2}}\right) \left(1, 1, 0 \right)$ Pa is applied to the upper surface, where the magnitude $|\bb{T}|$ is defined in terms of a dimensionless load factor $\mathcal{F}$ as
%In the current study, $\mathcal{F} = 1$.
A neo-Hookean hyperelastic material is assumed with $E = 15.293$ MPa, $\nu = 0.3$ and density $\rho = 1000$ kg m$^{-3}$, while the area $A = 0.04$ m$^2$ and the second moment of area $I = \frac{1}{7\,500}$ m$^4$. %0.0001333
The geometric and material parameters were chosen for the first natural frequency to be 1 Hz in the small strain limit.
The magnitude of the applied traction was chosen to ensure significant geometric nonlinearity, with the upper surface of the beam expected to drop below the plane of the lower surface.
Four succesively refined hexahedral meshes are generated using the OpenFOAM \texttt{blockMesh} utility, with cell counts of 270, $2\,160$, $17\,280$ and $138\,240$.
%A fixed time step size of 0.001617274174 s is chosen, corresponding to a Courant number of six on the mesh with $2\,160$ cells.
%A fixed time step size of 1 ms is chosen.
The time step size is 1 ms, and the total period is 10 s.
% corresponding to 10 expected oscillation periods.
%, corresponding to a Courant number of six on the mesh with $2\,160$ cells.

The deformed configuration of the beam at six time steps is shown in Figure \ref{fig:dynamic_cantilever}(a) for the mesh with $2\,160$ cells, where the upper surface is seen to drop below the horizontal from approximately t = 0.2 s to 0.32 s.
The corresponding displacement magnitude of the centre of the upper surface of the beam vs time is shown in Figure \ref{fig:dynamic_cantilever}(b).
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.5\textwidth]{figures/cantilever} 
	\subfigure[Displacement magnitude for t = $\left\{0, \, 0.1, \, 0.2\right\}$ s (translucent) and t = $\left\{0.3, \, 0.4, \, 0.5 \right\}$ s (opaque) for the mesh with $138\,240$ cells]
	{
	   \includegraphics[width=0.5\textwidth]{figures/cantilever_deformed}
   	} \quad
	\subfigure[Displacement magnitude of the centre of the upper surface of the beam vs time]
	{
	   \includegraphics[width=0.6\textwidth]{figures/cantilever_disp} 
   	   %\includegraphics[height=0.45\textwidth]{figures/cantilever_sigmaEq}  
   	}
   \caption{Deflection of a 3-D Cantilevered Beam}
   \label{fig:dynamic_cantilever}
\end{figure}
%\hl{It would be good to add a reference results, e.g. from FE}

@@

%\hl{maybe we should state the nonlinear/linear solver settings for completeness}

\paragraph{Case 7: Axial Turbine Blade}
This 3-D, quasi-static, small strain, linear elastic case consists of a twisted axial turbine blade (Figure \ref{fig:turbine_blade}) with the Cartesian axis-aligned bounding box $105.55\times177.628\times336.5$ mm.
This case demonstrates the application of the proposed approach to an industrially-relevant geometry.
The blade is constrained at the rotation axis end and subjected to a centrifugal body force $\bb{f}_b = \rho \omega^2 \bb{r}$ kg m$^{-2}$ s$^{-2}$.
The scalar rotational velocity $\omega = \frac{2\pi \text{RPM}}{60}$ is defined here about the $x$ axis, where $\text{RPM} = 720$.
The vector $\bb{r}$ is defined as the shortest vector to the rotation ($x$) axis.
The blade's root is constrained, while all other surfaces are traction-free.
A linear elastic material is assumed with $E = 4.431$ GPa, $\nu = 0.33$, and $\rho = 1200$ kg m$^{-3}$.
% while the area $A = (0.2)(0.2) = 0.04$ m$^2$ and the second moment of area $I = 0.0001333$ m$^4$.
An unstructured polyhedral mesh with $322\,161$ cells is employed (Figure \ref{fig:turbine_blade}), created in Ansys Fluent and converted to the OpenFOAM format using the \texttt{fluent3DMeshToFoam} OpenFOAM utility.
\hl{Could we include a finer mesh?}
%A fixed time step size of \hl{XXX} s is chosen, corresponding to a \hl{YY} on the coarsest mesh \hl{update as required}.
%The total time period is \hl{XXX} s, corresponding to \hl{XX} expected oscillation periods.
%\hl{An advantage of this case over the cantilever is that it is complex geometry; a disadvantage is that we do not have a reference solution}
%\hl{A mitigation for this disadvantage is we could run it in Abaqus to provide a credible reference}
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=\textwidth]{figures/turbine_blade_geometry.pdf} 
   \includegraphics[width=\textwidth]{figures/turbine_blade_geometry_mesh.pdf} 
   \caption{Axial turbine blade case geometry}
   \label{fig:turbine_blade}
\end{figure}

The prediction displacement magnitude distribution (left image in Figure \ref{fig:turbine_blade_disp_sigmaEq}) is consistent with a cantilever with the largest deflection occurring at the distal free-end of the turbine.
The equivalent (von Mises) stress distribution (right image in Figure \ref{fig:turbine_blade_disp_sigmaEq}) shows the peak stresses to occur near the blade root and leading and trailing edges, with concentrations near the trailing edge vortex generators \hl{correct name?}.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.8\textwidth]{figures/turbine_blade_disp_sigmaEq.pdf} 
   \caption{Axial turbine blade displacement magnitude and equivalent stress distributions \hl{non-smooth stress contours => indicative of low order of accuracy}}
   \label{fig:turbine_blade_disp_sigmaEq}
\end{figure}

@@

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Robustness and Resource Requirements}
\label{sec:resource_requirements}
%%--------------------------------------------------------------------------------------------------------------------%%
This section compares the robustness and resource requirements of the Jacobian-free Newton-Krylov and segregated approaches on the cases presented in Section \ref{sec:accuracy}.
Specifically, cases where either approach diverges are examined, and the time and memory requirements are presented.
In some cases, time and memory requirements from finite element software Abaqus are given for reference.
Time and memory requirements are implementation and hardware-specific; nonetheless, it is insightful to see the relative performances of the Jacobian-free Newton-Krylov and segregated approaches on the same hardware and within the same implementation framework.
% where several mesh densities are examined.
%Time and memory requirements from the classic segregated approach are given for comparison, along with the requirements from commercial finite element software Abaqus (version XXX): \hl{ask Dylan to create the Abaqus results when we are happy the paper will not change}.
%The finite element approach uses a coupled solution algorithm and direct linear solver, where a Newton-Raphson method is used for resolving nonlinearities.
%\hl{Take care when comparing times between different hardware}

Table \ref{tab:times_memory} lists the wall clock times (time according to a clock on the wall, rounded to the nearest second) and maximum memory usage according to the GNU time utility.
All clock times and memory usage were generated using a Mac Studio with an M2 Ultra CPU on one CPU core, where the code was built with the Clang compiler.
%\hl{Present data for one hardware first, and give comparison after.}
Examination of multi-CPU-core parallelisation is left to Section \ref{sec:parallelisation}.
\begin{table}[!htb]
	\centering
		\begin{tabular}{ll|ll|ll}
			\hline
			\textbf{Case} & \textbf{Cell Count} & \multicolumn{2}{c|}{\textbf{JFNK}} & \multicolumn{2}{c}{\textbf{Segregated}} \\
			     &            & \textbf{Time} & \textbf{Memory} & \textbf{Time} & \textbf{Memory} \\
			     &            & (in s) & (in MB) & (in s) & (in MB) \\
			\hline 
			\textbf{MMS} & 384 & 0 & $78$ 				& 0 & 79 \\
			\emph{2-D, static,}	& $4\,374$ & 0 & $86$ 			& 0 & 94 \\
			\emph{linear elastic} & $41\,154$ & 1 & $195$  		& 2 & 181 \\
				&  $355\,914$ & 4 & $1\,063$ 		& 9 & $1\,289$ \\
				& $2\,958\,234$ & 41 & $6\,724$ 	& 92 & $6\,174$ \\
				& $24\,118\,074$ & 486 & $30\,606$ & $1\,732$ & $30\,601$ \\
			\hline
			\textbf{Elliptic} & 45 & 0 & $72$ & 0 & 76 \\
			\textbf{Plate} & 472 & 0 & $78$ & 0 & 81 \\
			\emph{3-D, static,} & $4\,140$ & 1 & $153$ & 8 & 124 \\
			\emph{linear elastic} & $34\,968$ & 7 & $754$ & 149 & 660 \\
				& $287\,280$ & 95 & $3\,943$ & $2\,694$ & $3\,661$ \\
				& $2\,438\,242$ & 988 & $21\,884$ &  &  running (increase snes-max-funcs)\\
			\hline
			\textbf{T-member} & 624& 0 & 84 					&  1 & 85 \\
			\emph{3-D, static,} & $4\,992$ & 1 & 127 				&  7 &  141 \\
			\emph{linear elastic} & $39\,936$ & 10 & 557			& 133 & 723  \\
				& $319\,488$ & 154 & $4\,024$ 				&  & running  \\
				& $2\,555\,904$ & $1\,751$ & $22\,814$ 			&  &  \\
			\hline
			\textbf{Ventricle} & $1\,620$ & 54 & 133 				& & running \\
			\emph{3-D, static,}& $12\,960$ & 576 & 553 			& & \\
			\emph{hyperelastic} & $103\,680$ & $8\,362$ & $3\,435$ 	& & \\
				& $829\,440$ & $150\,023$ & $11\,746$ 			& & \\
			\hline
			\textbf{Membrane i} & 9 & 0 & 77 	& 0 & 76 \\
			\emph{2-D, static,}& 36 & 0 & 77  	& 0 & 76 \\
			\emph{linear elastic}& 144 & 0 & 78  & 0 & 78 \\
				& 576 & 0 & 82 				& 1 & 84 \\
				& $2\,304$ & 0 & 94 			& 4 & 102 \\
				& $9\,216$ & 1 & 152 		& 33 & 186 \\
				& $36\,864$ & 2& 497 		& & running \\
				& $147\,456$ & 10& $1\,461$ 	& & \\
			\hline
			\textbf{Membrane ii} & 9 & x & x 	& 1 & 78 \\
			\emph{2-D, static,} & 36 & x & x 	& 2 & 78 \\
			\emph{hyperelastic} & 144 & x & x 	& 5 & 80 \\
				& 576 & x & x 			& 26 & 91 \\
				& $2\,304$ & x & x 		& & running \\
				& $9\,216$ & x & x 		& & \\
				& $36\,864$ & x & x 		& & \\
				& $147\,456$ & & $x$ 	& & \\
			\hline
			\textbf{Membrane iii} & 9 & x & x 		& 3 & 78 \\
			\emph{2-D, static,} & 36 & x & x 		& 6 & 79 \\
			\emph{hyperelastoplastic}& 144 & x & x	& 27 & 82 \\
				& 576 & x & x			& & running \\
				& $2\,304$ & x & x 		& & \\
				& $9\,216$ & x & x 		& & \\
				& $36\,864$ & x & x 		& & \\
				& $147\,456$ & & $x$ 	& & \\
			\hline
			\textbf{Cantilever} & $270$ & 11 & 85 		& & all diverged \\
			\emph{3-D, dynamic,} & $2\,160$ & 71 & 181 	& & \\
			\emph{hyperelastic}& $17\,280$ & 854 & 752 	& & \\
				& $138\,240$ & $11\,800$ & $5\,790$ 	& & \\
			\hline
			\textbf{Turbine} & $322\,161$ & $2\,386$ & x & & decide on meshes \\
			\emph{3-D, static,} & & & & & \\
			\emph{linear elastic} & & & & & \\
			\hline
			\textbf{FSI} & $1\,252$ + 156 & $4\,265$ & 743 				& $4\,820$ & 752 \\
			\emph{2-D, dynamic,}	& $5\,008$ + 624 & $33\,366$ & 788 	& $46\,328$ & 786 \\
			\emph{hyperelastic} & $20\,032$ + $2\,496$ & $154\,237$ & 729 	& & \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage for Jacobian-free Newton-Krylov (JFNK) and segregated methods. Resource requirements are shown for the following cases: manufactured solution (MMS), XX }
	\label{tab:times_memory}
\end{table}

\hl{Comment on: Robustness, Time, Memory}
\hl{Comment on the effect of items in list at the start of this section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Truncation Error Analysis of the Rhie-Chow Stabilisation Term}
\label{app:RhieChow}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hl{Add this for 1-D}
